\chapterspecial{Referências}{}{}

\begingroup

\small
\begin{itemize}
\item
  \versal{ACNUR} (2001) \emph{Greece: \versal{UNHCR} concerned at conditions in new
  refugee sites and urges that alternatives be found}. Disponível em:
  goo.gl/Ac7wv2 (Acesso: 12 de outubro de 2016).
\item
  \versal{ACNUR} (2015) \emph{Refugees/Migrants Emergency Response ---
  Mediterranean}. Disponível em: goo.gl/Cyur5j (Acesso: 29 de novembro
  de 2016).
\item
  \versal{ACNUR} (2017) \emph{\versal{UNHCR} refugees/migrants emergency response ---
  Mediterranean}. Disponível em: goo.gl/31yJ59 (Acesso: 08 de janeiro de
  2017).
\item
  Anistia Internacional (2015) \emph{Hungary: \versal{EU} must formally warn
  Hungary over refugee crisis violations}. Disponível em: goo.gl/{STE}ca4
  (Acesso: 12 de outubro de 2016).
\item
  Anistia Internacional (2016a) \emph{Iran 2015/2016}. Disponível em:
  goo.gl/r81owM (Acesso: 16 de janeiro de 2017).
\item
  Anistia Internacional (2016b) \emph{Refugees shamefully trapped in
  Greece ---} \emph{amnesty urgent actions}. Disponível em:
  goo.gl/{BM}a3Ak (Acesso: 12 de outubro de 2016).
\item
  \versal{BBC} (2016) \emph{What}\emph{'}\emph{s happening in Aleppo?} Disponível
  em: goo.gl/lNt0Pi
  bbc.com/news/world"-middle"-east-38132163 
  (Acesso: 8 de Janeiro de 2017)
\item
  \versal{BBC} (2016a) \emph{Aleppo battle: Syrian city} \emph{`}\emph{back under
  government control}\emph{'}. Disponível em: goo.gl/bc3H98 (Acesso: 8
  de Janeiro de 2017).
\item
  Conselho Dinamarquês para Refugiados (2016) \emph{Summary of regional
  migration trends middle east (march, 2016)}. Disponível em:
  goo.gl/\versal{ZFM}9V0 (Acesso: 12 de outubro de 2016).
\item
  Deutsche Welle (2015) \emph{Hungary sues \versal{EU} at European court of
  justice over migrant quotas \textbar{} news \textbar{} \versal{DW}.\versal{COM}
  \textbar{} 03.12.2015}. Disponível em: goo.gl/1cAc1T (Acesso: 6 de
  novembro de 2016).
\item
  European Commission (2015) \emph{Refugee crisis} \emph{--} \emph{Q\&A
  on emergency relocation}. Disponível em: goo.gl/{WJ}0{RTK} (Acesso: 8 de
  novembro de 2016).
\item
  European Commission (2016) \emph{Commissioner Avramopoulos in
  Idomeni}. Disponível em: goo.gl/Mpe88n (Acesso: 15 de outubro de
  2016).
\item
  European Council --- Council of the European Union (2016)
  \emph{\versal{EU}"-Turkey statement, 18 march 2016}. Disponível em:
  goo.gl/wtk\versal{MT}x (Acesso: 30 de novembro de 2016).
\item
  European Commission (2016b) \emph{\versal{EU} and turkey agree European
  response to refugee crisis --- European commission}. Disponível em:
  goo.gl/e2naq4 (Acesso: 30 de novembro de 2016).
\item
  European Parliament and the Council of European Union (2015) Directive
  2013/33/\versal{EU} of the European Parliament and of the Council of 26 June
  2013 laying down standards for the reception of applicants for
  international protection. F.G.V\, Sweden (no. 43611/11) {[}2016{]}.
\item
  Goitom, H\, e Biblioteca do Congresso dos \versal{EUA} (2014) \emph{Laws
  criminalizing Apostasy}. Disponível em: goo.gl/4gk{AC}6 (Acesso: 16 de
  janeiro de 2017).
\item
  Hirschon, R\,(1998) Heirs of the Greek catastrophe: The social life of
  Asia Minor refugees in Piraeus. New York: Berghahn Books.
\item
  Kingsley, P\,(2016) \emph{Hungary}\emph{'}\emph{s refugee referendum
  not valid after voters stay away}. Disponível em: goo.gl/Ns0Md4
  (Acesso: 6 de novembro de 2016).
\item
  Médecins Sans Frontières (2016) \emph{\versal{MSF} to no longer take funds from
  \versal{EU} member states and institutions}. Disponível em:
  goo.gl/dYfZVg
  %msf.org.uk/article/msf"-no"-longer"-take"-funds"-eu"-member"-states"-and"-institutions
  (Acesso: 8 de novembro de 2016).
\item
  \versal{MSF} International. 2016.
  \emph{{\#Greece}}\emph{:
  Around 14,000 migrants \& refugees are currently trapped in}
  \emph{{\#Idomeni}}\emph{.
  We did over 2,000 medical consultations in one week in
  \versal{MSF} [Twitter]. }8 de março. Disponível em: goo.gl/jrXq{QM} {[}Acesso:
  12 outubro de 2016{]}.
\item
  Nianias, H\,(2016) \emph{Refugees in Lesbos: Are there too many \versal{NGO}s
  on the island?} Disponível em: goo.gl/9{OG}l{AJ} (Acesso: 25 de outubro de
  2016).
\item
  Organização Internacional de Migração (2017) \emph{Missing migrants
  project}. Disponível em: goo.gl/wF40Lo (Acesso: 08 de Janeiro de
  2017).
\item
  Organização Internacional de Migração (2017a) \emph{Relocation updated
  28 December 2016}. Disponível em: goo.gl/qkx{GMW} (Acesso: 8 de Janeiro
  de 2017).
\item
  Press Office of the Spokesperson for the Management of the Refugee
  Crisis, (2016). \emph{Request for comments on Idomeni and refugees in
  Greece --- Brazilian Book}. {[}email{]}.
\item
  Republic of Turkey Ministry of Foreign Affairs (2011) \emph{Lausanne
  Peace Treaty \versal{VI}. Convention Concerning the Exchange of Greek and
  Turkish Populations Signed at Lausanne, January 30, 1923}. Disponível
  em: goo.gl/{UC}rAuj (Acesso: 4 de novembro de 2016).
\item
  Serviço de Imigração Dinamarquês (2014) \emph{Update on the Situation
  for Christian Converts in Iran}. Available at: goo.gl/sVhanX (Acesso:
  16 de janeiro de 2017).
\item
  Smith, H\,(2016) \emph{Refugees in Greek camps targeted by mafia
  gangs}. Disponível em: goo.gl/00{STIA} (Acesso: 6 de novembro de 2016).
\item
  The Editors of Encyclopaedia Britannica (2016) `Greco"-Turkish wars
  \textbar{} Balkan history', em \emph{Encyclopaedia} \emph{Britannica}.
  Disponível em: goo.gl/CikJgU (Acesso: 4 de novembro de 2016).
\item
  The Editors of Encyclopaedia Britannica (2016) `Treaty of Sevres
  \textbar{} allies"-turkey {[}1920{]}', em \emph{Encyclopaedia
  Britannica}. Disponível em: goo.gl/Et7{JE}e (Acesso: 4 de novembro de
  2016).
\item
  The Guardian (2016) \emph{Aleppo must be}
  \emph{`}\emph{cleaned}\emph{'}\emph{, declares Assad, amid outcry over
  bloody siege}. Disponível em: goo.gl/hW2m4m (Acesso: 15 de outubro de
  2016).
\item
  Townsend, M\,(2016) \emph{'}\emph{Sexual assaults on children}\emph{'}
  \emph{at Greek refugee camps}. Disponível em: goo.gl/{VC}1O2M (Acesso: 6
  de novembro de 2016).
\end{itemize}
\endgroup